\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning \versionline{4}

### 2015-09-03 ICRA2016/bandits_docs/includes/abstract.tex
First full version of the paper with committed adobe illustrator figures

\begin{abstract}
\TODO{Fill in after rest of paper done.}
\end{abstract}

>>>>

\begin{abstract}
%\TODO{Adapted from flyer, probably needs to be toned down}
Advances in Big Data and distributed computing, combined with very large datasets of images and human speech, have produced a series of  data-driven results that surpass decades of research in analytic methods and, in some cases, that surpass human ability.
For example, deep neural networks can now learn to play video games, recognize faces, and translate between languages.
This raises the question: can Big Data and computation produce analogous advances in robot grasping and manipulation?
We introduce the Dexterity-Network (Dex-Net) 1.0, a Cloud-based dataset of 3D object models labelled with parallel-jaw grasps and similarity between objects and grasps based on multi-view Convolutional Neural Networks (CNNs) and grasp heightmaps.
We use Dex-Net in Multi-Armed Bandit (MAB) algorithms to quickly find a grasp with high probability of force closure on an object from a set of 250 candidates. 
We extend previous MAB models to predict grasp quality using similiarity to prior objects and grasps in Dex-Net using Continuous Correlated Beta Processes (CCBPs).
Our initial results suggest that using prior objects from Dex-Net can accelerate grasp planning by up to $10\times$.
%\TODO{More concrete results here as I organize them} 
Code, data, and additional information can be found at: \TODO{Url}
\end{abstract}

### 2015-09-03 ICRA2016/bandits_docs/includes/algorithm.tex
First full version of the paper with committed adobe illustrator figures

\section{Algorithm}

\TODO{Brief section on the high-level algorithm using the model: grasp sampling, evaluation of grasps, thompson sampling}

>>>>

\section{Grasp Selection Algorithm}
\seclabel{algo}

Our full algorithm for grasp selection using Multi-Armed Bandits (MABs) with prior grasp and object data from Dex-Net is detailed in Algorithm~\ref{alg:full}.
We first generate a set of candidate grasps $\mG$ for object $\mO$ and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting the next grasp using Thompson sampling, evaluating each grasp using force closure as described in \secref{quality}, and updating the Beta belief parameters for each grasp.
Finally, we return the grasp that has the highest mean prediction.

\begin{algorithm}
{\small
    \SetAlgoLined
    {\bf Input:} Object $\mO$, Number of Candidate Grasps $K$, Database of Prior Knowledge $\mD$, Maximum Iterations $T$, \\ Prior beta shape $\alpha_0$, $\beta_0$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
    \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}

    \tcp{Generate candidate grasps and priors}
	$\mG$ = AntipodalGraspSample($\mO, K$) \;
	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
	\For{$\bg_k \in \mG$}{
		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD$)\; 
		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
	}

	\tcp{Run MAB with Thompson Sampling}
	\For{$t = 1, .., T$}{
		$j = $ SelectNextIndex($\mA_{t-1}, \mB_{t-1}$)\;
		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
		$F_{j} = $ EvaluateForceClosure($\bg_j, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, F_j, \mG$)\; 
	}

	\tcp{Find grasp with max estimated quality}
	$\mU = \left\{ \mu_j = \frac{\alpha_{j,T}}{\alpha_{j,T} + \beta_{j,T}} \big| j = 1, ..., K \right\}$\;
	$j^*$ = $\myargmax{j = 1, ..., T} \mu_j$\;
	return $\bg_j$\;
    \caption{Grasp Selection With Multi-Armed Bandits Using a Database of Prior Knowledge}
    \label{alg:full}
}
\end{algorithm}

\subsection{Grasp Candidate Generation}
\seclabel{candidates}
In past work, Laskey et al.~\cite{laskey2015bandits} sampled candidate grasps in 2D by sampling a grasp center from an isotropic Gaussian ceneterd at the object center of mass and sampling a grasp angle uniformly at random.
However, this method is problematic in 3D because many of the samples may be oriented away from the object and the grasps may not adequately cover the entire surface of the object.

In this work, we use a modified version of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
Let $K$ be the number of grasps to sample, $w$ be the maximal opening of the gripper, $\gamma$ be an estimate of the friction coefficient, and $\mC = \{ \by \in \bR^3 \big| | f(\by) | < \epsilon$ be the set of points on the object surface for threshold $\epsilon$ and object SDF $f$.
To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly at random from $\mC$, which can be done using rejection sampling.
Next we form the friction cone $\mF_1$ at $\bc_1$ as described in \secref{contact} and sample a direction $\bv$ uniformly at random from the cone.
We then compute
\vspace{-2ex}
\begin{align*}
	\bc_2 &= \minimum{t \geq 0} t \text{ such that } | f\left(\bc_1 + (w / 2 - t) \bv \right) | < \epsilon \\
	\bx &= 0.5 (\bc_1 + \bc_2)
\end{align*}
\noindent similar to the contact computation of \secref{contact} and form the friction cone $\mF_2$ at contact $\bc_2$.
This yields a grasp $\bg = [\bx, \bv]^T$.
We add $\bg$ to our candidate set if $-\bv \in C\mF_1)$ and $\bv \in C(\mF_2)$, where $C(\mF) = \{ \by = t \bbf \big| t \in [0, \infty], \bbf \in Conv(\mF)\}$ is the convex cone for friction cone $\mF$.

\subsection{Thompson Sampling}
\seclabel{thompson}

Following Laskey et al.~\cite{laskey2015bandits}, we use Thompson sampling to select the next grasp to evaluate given belief distributions on the probability of force closure for each arm specified by estimates $\mA_t = \{\alpha_{1,t}, ..., \alpha_{K,t}\}$ and $\mB_t = \{\beta_{1,t}, ..., \beta_{K,t}\}$ at iteration $t$.
Thompson sampling samples a probability of force closure $\hat{\theta}_{j,t} \sim B(\alpha_{j,t}, \beta_{j,t})$ for all grasps $j = 1, ..., K$, then selects the grasp $j_t^* = \myargmax{j} \hat{\theta}_{j,t}$ to evaluate next.
Several other criteria exist for selecting the next evaluation in MAB, such as Gittins indices~\cite{laskey2015bandits}, Upper Confidence Bounds~\cite{boularias2015learning}, and Expected Improvement~\cite{montesano2012active}.

### 2015-09-03 ICRA2016/bandits_docs/includes/background.tex
First full version of the paper with committed adobe illustrator figures

\section{Continuous Correlated Beta Processes}
\seclabel{background}

We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.

\subsection{Beta-Bernoulli Processes}

Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

\noindent This combination of indepdent Bernoulli random variables with Beta priors is known as a {\it Beta-Bernoulli process}.

Let our prior distribution on $\theta_k$ be a beta distribution with parameters $\alpha_{k,0}$, $\beta_{k,0}$.
Then after observing force closure for $t$ samples $F_{1}(g_k), ..., F_{t}(g_k)$ from our uncertainty model, our posterior distribution on the Bernoulli success probability $\theta_k$ is obtained using Bayes rule.
This yields~\cite{laskey2015bandits}

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{i=1}^t F_{i}(g_k) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{i=1}^t (1 - F_{i}(g_k))
\end{align*}

\noindent Therefore the belief distribution on the probability of force closure $\theta_k$ can be updated by incrementing the value of $\alpha$ and $\beta$ for each force closure observed.
The expected value of $\theta_k$ after the observations is

\begin{align*}
	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
\end{align*}

Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.

A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
Then the CCBP posterior update for $\theta_k$ is~\cite{}:

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
\end{align*}

\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.

>>>>

\section{Correlated Multi-Armed Bandit Model}
\seclabel{background}

Finding an approximate solution of Equation~\ref{eq:objective} with Multi-Armed Bandits requires a predictive model of the probability of force closure for each grasp.
We use Continuous Correlated Beta Processes (CCBPs) to model force closure for a grasp as a Bernoulli random variable with correlations across grasps and objects~\cite{goetschalckx2011continuous, montesano2012active}.
\figref{correlated-motivation} illustrates how using a correlated model can lead to accelerated convergence of bandit algorithms.
%In practice, correlations may occur between two grasps that contact the same shape in similar locations, or between grasps on different shapes, such as grasping the handle of a mug and the handle of a teapot.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.22]{figures/illustrations/correlated_bandits.png}
\caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle. (Top Right) The true probability of force closure $P_F$ as a function of the angle of the grasp axis. (Middle Left) Uncorrelated MAB models maintain an estimate of $P_F$ independently for each grasp, indicated by bars and their height. On iteration $T$ of a MAB algorithm, the evaluated grasp (green bar) is force closure for samples . (Middle Right) Only the estimate of $P_F$ for the sampled grasp is updated on iteration $T+1$, and the grasp with highest estimated $P_F$ remains suboptimal. (Bottom Left) Correlated MAB models maintain a global predictive function (red) of $P_F$ for any possible grasp but may select grasps from a set of discrete candidates (indicated by dots). (Bottom Right) On iteration $T+1$, the evaluated grasp (green dot) is sampl returns force closure and the global model is updated, increasing the estimated $P_F$ for ``nearby" grasps. Although a suboptimal grasp was sampled, the global model now correctly predicts the optimal grasp in the set. }
\figlabel{correlated-motivation}
\vspace*{-15pt}
\end{figure}

Continuous Correlated Beta Processes (CCBPs) were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in MAB problems~\cite{chu2011contextual}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar, such as a grasp on the handle of a mug and the handle of a teapot.

We are interested in solving Equation~\ref{eq:objective} for a new object $\mO_i$.
Let $\mG_{i}$ be a set of $K$ candidate grasps for $\mO_i$, $\Gamma_i = \{\bg_{i,k}\}_{k=1}^K$.
We define $F_{j,\ell} = F(\bg_{j,\ell}) \in \{0, 1\}$ an occurence of force closure on an evaluation of any grasp $\bg_{j,\ell}$ on object $\mO_j$ using samples of object pose, gripper pose, and friction, as described in \secref{quality}.
Then let $N_{j,\ell}$ be the number of total evaluations of for grasp $\bg_{j,\ell}$, and define $S_{j,\ell} = \sum_{a=1}^{N_{j,\ell}} F_{j,\ell}$ to be the total number of times force closure has been observed for any grasp.
Futhermore let $\mD = \{ N_{j,\ell}, S_{j,\ell}, \mY_{j,\ell} = (\bg_{j,\ell}, \mO_j) \big| j = \{1, ..., M\}, \ell \in \{1, ..., K\} \}$ be a discrete set of $M$ known objects stored in a database, each with a discrete set of $K$ candidate grasps $\Gamma_j = \{\bg_{j,\ell}\}_{\ell=1}^K$ and $N_{j,\ell}$ and $S_{j,\ell}$ for each object.

%and let $\mS = \{ S_{j,\ell} \big| j \in \{1, .., M\}, \ell \in \{1, ..., K\} \}$ be the history of force closure observations for all grasps and all objects in the database.

We model force closure for each candidate grasp, $F_{i,k}$, as a Bernoulli random variable with probability of success $\theta_{i,k}= P_F(\bg_{i,k})$.
Since we do not know the value of $\theta_{i,k}$, we maintain a belief distribution for each $\theta_{i,k}$ based on our prior belief about the likelihood of force closure.
In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

A CCBP estimates the shape parameters for a grasp and object $\mY_{i,k} = (\bg_{i,k}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
In this work we use a unit-bandwidth squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} w_m^2 \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_2^2 \right)
\end{align*}
\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space and $w_m \in \mathbb{R}$ are weights scaling the relative contribution of the feature maps to the similarity metric.

Before the first iteration of the MAB algorithm, we update our belief for each candidate grasp to its similarity to all grasps and objects from the database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
%\vspace{-2ex}
\begin{align}
	%p \left(\theta_{i,k} | \mS, \mN \right) &= \betadist\left( \alpha_{i,k,0}, \beta_{j,k,0} \right) \notag \\
	\alpha_{i,k,0} = \alpha_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K k(\mY_{i,k}, \mY_{j,\ell}) S_{j,\ell} \label{eq:alpha-prior} \\
	\beta_{i,k,0} = \beta_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K  k(\mY_{i,k} \mY_{j,\ell}) (N_{j,\ell} - S_{j,\ell}) \label{eq:beta-prior}
\end{align}
\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits}.
% and $\mS$ and $\mN$ are the number of successes and total trials for grasps in the database, respectively.
Upon observing $F_{i,k}$ for grasp $\bg_{i,k}$ on iteration $t$, we update our belief $\theta_{j,k}$ for all other grasps on object $\mO_i$ by~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	\alpha_{j,k,t} &= \alpha_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) F_{i,k} \label{eq:alpha} \\
	\beta_{j,k,t} &= \beta_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) (1 - F_{i,k})\label{eq:beta}
\end{align}

\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.

\subsection{Feature Mappings}
We use a set of feature mappings $\phi_1, ..., \phi_{N_f}$ to capture similarity based on grasp parameters, local surface geometry, and global object shape.

\subsubsection{Grasp Parameters}
\seclabel{param-features}
Since grasps may be correlated across small changes to the grasp center and approach direction on a single shape, we use the feature maps $\phi_{x}(\mY) = \bx$ and $\phi_{v}(\mY) = \bv$, the identity transformations for the grasp center and axis.
Additionally we use the moment arm feature map $\phi_{\rho}(\mY) = [ \| \rho_1 \|_2, \| \rho_2 \|_2]^T \in \bR^2$ because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
However, similarity between grasp centers and approach directions may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar.
For example, consider two grasps that contact a box near the corner.
The two grasps may have similar parameters and moment arms but may contact the surface on different sides of the edge, resulting in different surface orientations at the contact points.

\subsubsection{Grasp Heightmaps}
\secref{local}
We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging}.
Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
Then we assign the heightmap value
\begin{align*}
	\bh_k(u,v) = \minimum{t \geq -r} t \text{ such that } | f\left( \bp_k(u,v) + s_k \bv \right) | < \epsilon
\end{align*}
 where $s_1 = -1$, $s_2 = 1$, $\epsilon$ is the surface threshold used for finding contacts, and $f$ is the SDF of object $\mO$. 
Finally, we make the heightmap rotationally invariant by rotating it to align the axes with the eigenvectors of the weighted covariance matrix of contact points generating the heightmap as described in~\cite{tombariunique}.
Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$. \TODO{This is slightly more complicated but takes a bit to explain; basically the ordering of contacts doesn't matter here}
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
\caption{Three local surface heightmaps extracted on a teapot. Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.  }
\figlabel{local-feature-model}
\vspace*{-15pt}
\end{figure}

\subsubsection{Global Features}
\seclabel{cnn}
While force closure is based on local surface properties of an object around contact points, measuring global similarity may be similarity may be useful for two reasons.
First, the sums in Equations~\ref{eq:alpha-prior} and~\ref{eq:beta-prior} may be expensive when the database is large, and global object similarity can be used to sum over only the objects that are grasped similarity to a new object of interest.
Second, the heightmaps may not capture all possible contact points for a grasp under perturbations in object and gripper pose.

%\TODO{Justify why class labels help, if they do}
We measure global similarity between objects using a feature mapping derived from multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval.
\figref{global-feature-model} illustrates our method.
Let $R$ be the maximum dimension of the object bounding box.
We first render every object on a white background in a total of $N_c$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{\pi}{N_c}$ and $\delta_{\phi} = \frac{\pi}{2 N_c}$ and radii $r = R, 2R$.
Then we train a deep CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict a class label for the rendered images based on known class labels for the 3D models using Stochastic Gradient Descent (SGD).
Next, we pass each of the $N_c$ views of each object through the finetuned CNN and max-pool the output of the fc7 layer.
We finally use Principal Component Analysis (PCA) to reduce the max-pooled output to from 400 dimensions to 100 dimensions.
This yields a representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object, and thus our final feature map is $\phi_{g}(\mY) = \psi(\mO)$.
In our implementation, we trained the multi-view CNN on rendered images of 171 classes of 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, which had a test accuracy of 76\%.

%\TODO{Expand above paragraph, include more details on method as well as the results of training}

\begin{figure}[t!]
\centering
\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty. We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture. Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
\figlabel{global-feature-model}
\vspace*{-15pt}
\end{figure}

\subsection{Optimizing Feature Weights}
One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
%Past work has optimized these weights using a squared error loss on the probability of success predicted by the CCBP and a true probability of success from brute force evaluation~\cite{montesano2012active}.
%However, this criterion may be inappropriate for predicting probabilities, as the predictions must be bounded between 0 and 1.
We select the weights that minimize the cross entropy loss~\cite{}:

\begin{align*}
	w_1^*, ..., w_{N_f}^* = \myargmin{w_1, ..., w_{N_f} \geq 0} \frac{1}{M} \sum \limits_{i=1}^M &\mu_i \log \left( \frac{\alpha_i}{\alpha_i + \beta_i} \right) + \\  &(1 - \mu_i) \log \left( \frac{\beta_i}{\alpha_i + \beta_i} \right)
\end{align*}
\noindent where $\alpha_i$ and $\beta_i$ are the posterior shape parameters given by Equations~\ref{eq:alpha-prior} and~\ref{eq:beta-prior} and $\mu_i$ is the probability of force closure evaluated by exhaustive Monte-Carlo integration for a set of $M$ grasps.
We optimize this objective using SGD with the weights initialized to $w_i = 100$ for all $i$.
\TODO{For experiments so far we actually use a grid search and not SGD but we are interested in using this.}
